### 2023-07-19 writing/manuscript.Rmd
Fixing `kableExtra` bug

---
bibliography: themusiclab.bib
csl: pnas.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{mdframed}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
- \usepackage{rotating}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
link-citations: yes
output:
  pdf_document:
    number_sections: yes
  word_document:  
  html_document:
    df_print: paged
---

@@

kable(manual_table1,
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      linesep = "",
      col.names = c("Language family","Language","Total $n$","Subregion","Country","Country-wise $n$"),
      longtable = TRUE,
) %>% 
  # partial horizontal lines
  row_spec(c(1,8,10,11,14,15,16,18,23,25,35,37,38,39,41,42,43,47,48), extra_latex_after = "\\cline{2-6}") %>%
  row_spec(c(3,6,21,24,26:30,33,34,36,40,44,45,46,54), extra_latex_after = "\\cline{4-6}") %>%
  # full horizontal lines
  row_spec(c(7,9,12,49,50,51,53,55), hline_after = TRUE) %>%
  kable_styling(font_size = 8,
                full_width = FALSE) %>%
  footnote(general = "Linguistic and geographic information about the participants in the web-experiment. The ``Language'' column denotes the native language spoken by the participant (and the language they completed the experiment in); the ``Total n'' column denotes the number of participants recruited for that language; the ``Language Family'' column denotes the language family this particular language is part of, as per the Glottolog system (40). Glottolog is a comprehensive catalogue of the world's languages and their genealogy, and can be accessed at https://glottolog.org. Within each language, participants were recruited from multiple countries, as noted in the ``Country'' column. For the cultural proximity analyses, participants were then grouped into geographic subregions based on their reported location, as per the Human Relations Area Files World Sub-region typology. The ``Country-wise n'' column indicates the number of participants per language in each country.",
           general_title = "Table 1.",
           footnote_as_chunk = TRUE,
           title_format = "bold",
           escape = FALSE,
           threeparttable = TRUE)

>>>>

---
bibliography: themusiclab.bib
csl: pnas.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{mdframed}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
- \usepackage{rotating}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
link-citations: yes
output:
  pdf_document:
    number_sections: yes
---

@@

kable(manual_table1,
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      linesep = "",
      col.names = c("Language family","Language","Total $n$","Subregion","Country","Country-wise $n$"),
      longtable = TRUE,
) %>% 
  # partial horizontal lines
  row_spec(c(1,8,10,11,14,15,16,18,23,25,35,37,38,39,41,42,43,47,48), extra_latex_after = "\\cline{2-6}") %>%
  row_spec(c(3,6,21,24,26:30,33,34,36,40,44,45,46,54), extra_latex_after = "\\cline{4-6}") %>%
  # full horizontal lines
  row_spec(c(7,9,12,49,50,51,53,55), hline_after = TRUE) %>%
  kable_styling(font_size = 8,
                full_width = FALSE) %>%
  kableExtra::footnote(general = "Linguistic and geographic information about the participants in the web-experiment. The ``Language'' column denotes the native language spoken by the participant (and the language they completed the experiment in); the ``Total n'' column denotes the number of participants recruited for that language; the ``Language Family'' column denotes the language family this particular language is part of, as per the Glottolog system (40). Glottolog is a comprehensive catalogue of the world's languages and their genealogy, and can be accessed at https://glottolog.org. Within each language, participants were recruited from multiple countries, as noted in the ``Country'' column. For the cultural proximity analyses, participants were then grouped into geographic subregions based on their reported location, as per the Human Relations Area Files World Sub-region typology. The ``Country-wise n'' column indicates the number of participants per language in each country.",
           general_title = "Table 1.",
           footnote_as_chunk = TRUE,
           title_format = "bold",
           escape = FALSE,
           threeparttable = TRUE)
